\newpage
\section{Problem 2: Class Contacts (35 pts)}

\subsection{Description:}
Define a formal specification in Object-Z for class \textit{Contacts} whose interface contains the
following \textit{robust specifications}:

\begin{itemize}
    \item \textbf{MakeNewContact}: Adds a new person to Contacts with a single phone number.
    \item \textbf{AddNumber}: Adds an additional phone number for an existing contact.
    \item \textbf{SearchForNumber}: : Returns a collection of phone numbers for a given person.
    \item \textbf{DeleteNumber}: Deletes an existing number.
\end{itemize}

\subsection{Answer:}

\begin{class}{Contacts}
\also
\upharpoonright (MakeNewContact, AddNumber, SearchForNumber, DeleteNumber) \\
\begin{state}
numbers: \mathbb{P} PhoneNumberType\\
recorded : PhoneNumberType \rightarrow NameType\\
\where
numbers = dom~recorded
\end{state} \\
% INIT SECTION %
\begin{init}
recorded = \emptyset %\{ \}
\end{init} \\
% MakeNewContactOK  SECTION%
\begin{op}{MakeNewContactOK}
\Delta (recorded) \\
number?: PhoneNumberType \\
name?: NameType \\
\ST
number? \notin numbers \\
name? \notin ran~recorded \\
recorded' = recorded \cup \{number? \mapsto name? \}
\end{op}\\
% AddNumberOK SECTION %
\begin{op}{AddNumberOK}
\Delta (recorded, numbers) \\
number?: PhoneNumberType \\
name?: NameType
\ST
number? \notin numbers \\
name? \in ran~recorded \\
recorded' = recorded \cup \{number? \mapsto name?\} \\
numbers' = numbers \cup \{number?\} \\
\end{op}\\
\begin{op}{SearchForNumberOK}
\Xi () \\
\ST
\end{op}\\
\begin{op}{DeleteNumberOK}
\Delta () \\
\ST
\end{op}\\
\begin{op}{Success}
response!: Message \\
\ST
response! = 'ok'
\end{op}\\
\begin{op}{NumberExists}
number?: PhoneNumberType \\
response!: Message \\
\ST
number? \in numbers \\
response! = 'Number~already~exists'
\end{op}\\
\zbreak
\begin{op}{NameExists}
name?: NameType \\
response!: Message \\
\ST
name? \in ran~recorded \\
response! = 'Name~already~taken'
\end{op}\\
\also
MakeNewContact \sdef (MakeNewContactOK \wedge Success) \oplus (NumberExists \lor NameExists) \\
AddNumber \sdef (AddNumberOK \wedge Success) \oplus (NumberExists \lor \neg NameExists) \\
SearchForNumber \sdef \\
DeleteNumber \sdef
\end{class}
