\newpage


\section{Problem 8 (12 pts)}
\subsection{Description:}


Consider sets $A = \{1, 2, 3, 4, 5, 6 \}$ and $B = \{ a, b, c, d, e, f \}$.

\begin{enumerate}

\item Determine the type of the correspondence in each of the following cases, or indicate if the correspondence is not a function.

\begin{enumerate}
\item $\{ 1 \mapsto b, 2 \mapsto c, 3 \mapsto e, 4 \mapsto d, 5 \mapsto f, 3 \mapsto a \}$

\item $\{ 1 \mapsto a, 2 \mapsto d, 3 \mapsto a, 4 \mapsto f, 5 \mapsto d, 6 \mapsto c \}$

\item $\{ 1 \mapsto c, 2 \mapsto b, 3 \mapsto d, 4 \mapsto e, 5 \mapsto e, 6 \mapsto f  \}$

\item $\{ 1 \mapsto b, 2 \mapsto c, 3 \mapsto e, 4 \mapsto d, 5 \mapsto f, 6 \mapsto a \}$
\end{enumerate}

\noindent Fill in the table below, using $\checkmark$, or $\times$.

\begin{center}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
		& Injective		& Surjective	& Bijective 	& \multicolumn{1}{m{3cm}|}{Neither injective nor surjective}	&	Not a function	\\
\hline
(a)		& 		& 		& 	& 			&  \\
\hline

(b)		& 		& 		& 		& 	&	 \\
\hline


(c)		& 		& 		& 		& 	&  \\
\hline

(d)		& 		& 		& 		&	&  \\
\hline
\end{tabular}
\end{center}


\item Is it possible to construct a function $f : A \rightarrow B$ which is surjective and not injective?  Discuss.
\end{enumerate}

\subsection{Answer:}

\begin{enumerate}
    \item[]
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|}
\hline
		& Inective		& Surjective	& Bijective 	& \multicolumn{1}{m{3cm}|}{Neither injective nor surjective}	&	Not a function	\\
\hline
(a)		& 		& 		& 	& 			&$\checkmark$  \\
\hline

(b)		& 		& 		& 		& $\checkmark$	&	 \\
\hline


(c)		& 		& 		& 	& $\checkmark$	&  \\
\hline

(d)		& 		& 		&$\checkmark$ 		&	&  \\
\hline
\end{tabular}
\end{center}

	\item A function from $A$ to $B$ is an assisgnment of each element of the domain to exactly one element of the codomain.
	We know that a function is surjective if each of the elements of the codomain is mapped by at least one element of the domain.
	\\
	Therefore, if a function $f : A \rightarrow B$ is to be surjective, all elements of $A$ must point to one and only one 
	element of $B$ (definition of a function) and all elements of $B$ must be pointed by at least one element of $A$ (definition
	of a surjective function).
	\\
	Fianlly, we know that $A$ and $B$ have the same cardinality, namely 6. This yields that for $f$ to be surjective, all elements
	of $B$ have to be pointed by exactly one element of $A$, making $f$ an injective function. 
	\\
	In conclusion, given sets $A$ and $B$, it is impossible for a function $f : A \rightarrow B$ to be surjective without
	being injective.  
\end{enumerate}
